Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}

@@

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model:
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules are modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

@@

We believe that high resolution atmospheric recovery can be achieved
by a set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upward, performing integral imaging of the sky.
This paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

We simulate RT through the atmosphere using two models. The first is
based on Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}) and
models Multiple-Scattering. Therefore it enables simulating realistic
scenarios.  The second model uses the Single-Scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than the MC model
but it enables stating an analytic solution to the RT in a closed
form. This closed form is beneficial to us as it enables us to invert
the model and thus recover the underlying atmosphere
(\cref{sec:inverse-problem}). To mimic realistic scenarios, we apply
the reconstruction algorithm on images simulated by the MC model.

@@

A forward model takes as input the aerosol distribution, and outputs
images as if captured at various viewpoints.  We use a
\emph{single-scattering} model, in which any SR changes direction
(scatters) only once on the way to the camera. This model is valid in
atmospheres that are not very dense: inside fog and clouds this model
does not apply.

Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
capture the sky lightfield from below. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
  x}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
measured radiance in all locations ${\bm x}$ and angles
${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
  x},{\bm{\Theta}})$. Individual images are slices of the lightfield.

Under single-scattering approximation, radiative transfer has three
steps (\cref{fig:groundgrid}):
\begin{enumerate}
\item Attenuation of a SR propagating from the top of the atmosphere
  (TOA) to voxel $k$.
\item Light scattering at voxel $k$, towards a camera.
\item Light attenuation on the LOS from voxel $k$ to the camera.
\end{enumerate}

Steps 1 and 3 involve the optical depth along the light path to and
from voxel $k$, analyzed in \cref{sec:optical-depth}.  Step 2 involves
the scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.

>>>>

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}

@@

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model:
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules can be modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

@@

We believe that high resolution atmospheric recovery can be achieved
by a set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upward, performing integral imaging of the sky.
Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
capture the sky lightfield from below. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
  c}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
measured radiance in all locations ${\bm x}$ and angles
${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
  x},{\bm{\Theta}})$.This paper takes the first step, of formulating
this principle and demonstrating feasibility using realistic
simulations.  We simulate RT through the atmosphere using two
models. The first is based on Monte Carlo (MC) methods
(\cref{sec:monte-carlo-simul}) and models
Multiple-Scattering. Therefore it enables simulating realistic
scenarios.  The second model uses the Single-Scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than the MC model
but it enables stating an analytic solution to the RT in a closed
form. This closed form is beneficial to us as it enables us to invert
the model and thus recover the underlying atmosphere
(\cref{sec:inverse-problem}). To mimic realistic scenarios, we apply
the reconstruction algorithm on images simulated by the MC model.

@@

A forward model takes as input the aerosol distribution, and outputs
images as if captured at various viewpoints.  In a
\emph{single-scattering} model, any SR changes direction only once on
the way to the camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply.  Under
single-scattering approximation, radiative transfer has three steps
(\cref{fig:groundgrid}):
\begin{inparaenum}[\hfill\bfseries a\upshape)]
\item \label{itm:first} Attenuation of a SR propagating from the top
  of the atmosphere (TOA) to voxel $k$.
\item \label{itm:second} Light scattering at voxel $k$, towards a
  camera.
\item \label{itm:third} Light attenuation on the LOS from voxel $k$ to
  the camera.
\end{inparaenum}
Steps \ref{itm:first} and \ref{itm:third} involve the optical depth
along the light path to and from voxel $k$, analyzed in
\cref{sec:optical-depth}.  Step \ref{itm:second} involves the
scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.
